---
title: "Multiple Linear Regression"
output: html_notebook
---

# BACKWARD ELIMINATION METHOD

# installing packages 

```{r}
# install.packages('caTools')
# install.packages('ggplot2')

library(ggplot2)
library(caTools)
```

# importing dataset

```{r}
dataset <- read.csv('50_Startups.csv')

dataset
```

# encoding categorical values (State)

```{r}
states <- unique(dataset$State) # get all unique values on State variable

dataset$State <- factor(
  dataset$State, # select column to encode 
  levels = states, # what values to encode
  labels = c(1: length(states)) # replacement values(range 1 - length of states)
)

dataset
```

# splitting dataset into training set and test set

```{r}
set.seed(123)
split <- sample.split(
  Y = dataset$Profit, # dependent variable
  SplitRatio = 0.8 # percentage of observations 80% for the training set 20% to the test set (recommended = 0.75)
)

training_set <- subset(dataset, split == TRUE)
test_set <- subset(dataset, split == FALSE)
```

```{r}
training_set
```

```{r}
test_set
```

# building the model (backward elimination method)

1. select significance level (P-value < 0.05) 
2. fit model with all possible predictors <-  formula = Profit ~ R.D.Spend + Administration + Marketing.Spend + State

```{r}
regressor <- lm(
  formula = Profit ~ R.D.Spend + Administration + Marketing.Spend + State,
  data = training_set,
)
summary(regressor)
```

3. consider the predictor with the highest P-value (State)
4. remove the predictor (State)
5. fit the model without the variable <- formula = Profit ~ R.D.Spend + Administration + Marketing.Spend,
```{r}
regressor <- lm(
  formula = Profit ~ R.D.Spend + Administration + Marketing.Spend,
  data = dataset,
)
summary(regressor)
```


6. consider the predictor with the highest P-value (Administration)
7. remove the predictor (Administration)
8. fit the model without the variable <- formula = Profit ~ R.D.Spend + Marketing.Spend,

```{r}
regressor <- lm(
  formula = Profit ~ R.D.Spend + Marketing.Spend,
  data = dataset,
)
# P-value of Marketing.Spend went down from 0.1 to 0.06 
# which can be considered to have a statistical significance
summary(regressor)
```

9. consider the predictor with the highest P-value (Marketing.Spend)
10. remove the predictor (Marketing.spend)
11. fit the model without the variable <- formula = Profit ~ R.D.Spend,

```{r}
regressor <- lm(
  formula = Profit ~ R.D.Spend,
  data = dataset,
)
summary(regressor)
```

model is ready

# predicting test set results

```{r}
# create a new set from test set excluding the Profit variable (profit is what we are trying to predict)
new_set <- test_set[,1:4]

y_pred <- predict(
  regressor,
  newdata = new_set
)
```
```{r}
new_set
```

```{r}
y_pred
```

# visualizing training set results

```{r}
ggplot() + 
  geom_point(
    aes(
      # dataset of what we are visualizing
      x = training_set$R.D.Spend,  
      y = training_set$Profit
    ),
    colour = 'red'
  ) + 
  geom_line(
    aes(
      # use regression from training 
      x = training_set$R.D.Spend, 
      predict(regressor, newdata = training_set)
    ),
    colour = 'blue'
  ) + 
  ggtitle('R.D.Spend vs Profit (Training Set)') + 
  xlab('R.D.Spend') + 
  ylab('Profit')
```

# visualizing actual test set results

```{r}
ggplot() + 
  geom_point(
    aes(
      # dataset of what we are visualizing
      x = test_set$R.D.Spend,  
      y = test_set$Profit
    ),
    colour = 'red'
  ) + 
  geom_line(
    aes(
      # use regression from training 
      x = training_set$R.D.Spend, 
      predict(regressor, newdata = training_set)
    ),
    colour = 'blue'
  ) + 
  ggtitle('R.D.Spend vs Profit (Test Set)') + 
  xlab('R.D.Spend') + 
  ylab('Profit')
```

# visualizing predicted test set results from new set

```{r}
ggplot() + 
  geom_point(
    aes(
      # dataset of what we are visualizing
      x = test_set$R.D.Spend,  
      y = y_pred # values of what we predicted
    ),
    colour = 'red'
  ) + 
  geom_line(
    aes(
      # use regression from training 
      x = training_set$R.D.Spend, 
      predict(regressor, newdata = training_set)
    ),
    colour = 'blue'
  ) + 
  ggtitle('R.D.Spend vs Profit Prediction (New Set)') + 
  xlab('R.D.Spend') + 
  ylab('Profit')
```


